\documentclass[master]{subfiles}
\begin{document}
\section{Research Question}
The research aims to answer the question: How is the performance of machine learning agent affected by different feature vectors in the game of schnapsen? The goal is to build a machine learning bot with additional features, make an investigation on how different features and lengths of feature vectors affect the game performance, time and results of the game. There are three possible outcomes of our research: when changes have no effect, positive effect, negative effect. The hypothesis is that the longer the feature vector, the more advanced cases of the game states the bot can comprehend and as a result, have a better winning rate is. An investigation is going to be made by comparing agents such as rand, bully, minimax, rdeep, alpha-beta, against the machine learning bot through tests that show how many wins each strategy has after playing against each other. As a result, machine learning bot has managed to get the highest win rate against other players. Moreover, the amount of time taken to win has been increasing. The results of the tests provided a strong incentive to conduct research about the machine learning algorithms and specific parts of the current state that had an impact on the winning rate. In the research, there are going to be used two definitions: default features and additional features. The default features are player’s 1 points, player’s 2 points, the player’s 1 pending points, player’s 2 pending points, trump suit, phase of the game, the size of the stock, leader, whose turn and card played by an opponent. Additional features are called all the features that were not mentioned in the default features.
\end{document}